Appendix for: Deep Reinforcement Learning for Conservation Decisions

### 2021-04-07 manuscript/appendix.Rmd
appendix pdf

```{r}
# Simulate management under the trained agent
TD3 <- sb3$TD3$load("cache/td3-conservation")
TD3_sims <- env$simulate(TD3, reps = 100L)
TD3_policy <- env$policyfn(TD3, reps = 10L)
```

>>>>

```{r}
# Simulate management under the trained agent
# See https://github.com/boettiger-lab/conservation-agents/blob/4baaa6c9b994085ca56c42364f7affcc58b0ef3b/conservation/TD3.py

TD3 <- sb3$TD3$load("cache/td3-conservation")
TD3_sims <- env$simulate(TD3, reps = 100L)
TD3_policy <- env$policyfn(TD3, reps = 10L)
```
